WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-08-14 ms.tex
Increment DCC version
Update runtimes

With just one thread, the \ac{BAYESTAR} analysis takes 87\nobreakdashes--384~s, already orders of magnitude faster than the full parameter estimation. With 32 threads, \ac{BAYESTAR} takes just 4\nobreakdashes--15~s. In practice, \ac{BAYESTAR}'s data handling (reading the detectors' \acp{PSD}, communicating with the \ac{GW} candidate database, writing FITS files) take an additional 15~s or so, though this overhead could be reduced by parallelizing many of these steps. The overall latency is comparable to the other stages (data aggregation, trigger generation, alert distribution) in the real\nobreakdashes-time \ac{BNS} analysis; therefore any significant further speedup would require significant changes through Advanced \acs{LIGO} computing and infrastructure. The 32\nobreakdashes-thread configuration is representative of how \ac{BAYESTAR} might be deployed in early Advanced \ac{LIGO}.\footnote{\ac{BAYESTAR} has been successfully ported to the Intel's Many Integrated Core~(MIC) architecture and has been tested in a 500 thread configuration on a system with dual Intel Xeon Phi 5110P coprocessors.} For comparison, sky localization with LALINFERENCE takes about 100 hours \cite{BerryLocalization}.

@@

\begin{acknowledgements}
This paper has LIGO Document Number LIGO\nobreakdashes-P1500009\nobreakdashes-v2.

>>>>

With just one thread, the \ac{BAYESTAR} analysis takes 76\nobreakdashes--356~s, already orders of magnitude faster than the full parameter estimation. With 32 threads, \ac{BAYESTAR} takes just 4\nobreakdashes--13~s. In practice, \ac{BAYESTAR}'s data handling (reading the detectors' \acp{PSD}, communicating with the \ac{GW} candidate database, writing FITS files) take an additional 15~s or so, though this overhead could be reduced by parallelizing many of these steps. The overall latency is comparable to the other stages (data aggregation, trigger generation, alert distribution) in the real\nobreakdashes-time \ac{BNS} analysis; therefore any significant further speedup would require significant changes through Advanced \acs{LIGO} computing and infrastructure. The 32\nobreakdashes-thread configuration is representative of how \ac{BAYESTAR} might be deployed in early Advanced \ac{LIGO}.\footnote{\ac{BAYESTAR} has been successfully ported to the Intel's Many Integrated Core~(MIC) architecture and has been tested in a 500 thread configuration on a system with dual Intel Xeon Phi 5110P coprocessors.} For comparison, sky localization with LALINFERENCE takes about 100 hours \cite{BerryLocalization}.

@@

\begin{acknowledgements}
This paper has LIGO Document Number LIGO\nobreakdashes-P1500009\nobreakdashes-v3.
